Buildtime Trend : What's trending in your build process

### 2015-03-31 buildtimetrend/presentation.tex
add example of matplotlib chart
add dashboard 0.1 example
add keen.io logo
improve text

    <show picture of matplotlib chart>

@@

    <insert Keen.io logo>

@@

    \frametitle{First release}
    Dashboard :\\
    <show picture of first dashboard>

@@

      \item storing in XML and chart generation with matplotlib (native mode)
      \item storing and chart generation with Keen.io

>>>>

    \includegraphics[scale=.45]{pictures/example_matplotlib_trend.png}

@@

    \includegraphics[scale=.20]{pictures/keenio_workflow.png}\\

@@

    \frametitle{First release - dashboard}
    \includegraphics[scale=.45]{pictures/example_dashboard.png}

@@

      \item storing data in XML and chart generation with matplotlib (native mode)
      \item storing data and chart generation with Keen.io
